Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-18 article_review/reviewer_letter.tex
Adding real case example
More reviewer changes

\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\vk}{\vect{k}}
\newcommand{\vx}{\vect{x}}
\newcommand{\vI}{\vect{I}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\wcS}{\widecheck{S}}
\def\dashfill{\cleaders\hbox to 2em{-}\hfill}

@@

\item[3.]The set C: In the section describing numerical results, choices are made for the parameters $\ell^*$ and $r$ which in turn define the set (cone) of functions C for which the error threshold formula (14) used to derive the algorithm holds. There should be some information in the paper on whether or not the functions considered in this section can be shown to be in this cone. This is especially important in light of the results obtained on page 10 (column 1, lines 36-38), where it looks like the error threshold was not met by the algorithm. Is it because the function is not in C?
\end{itemize}

@@

{\color{blue} The biased estimator has been replaced by the unbiased one.}
\item[c.] page 4, column 2, equation (14): it is not clear how $\ell$ is chosen on the RHS, and whether or not the inequality holds for all $\ell \leq m$ or for some specific value of $\ell$ ? Please clarify.
\item[d.] page 4, column 2, line 42: is it not instead "...the error bound $\epsilon_{\hat{I}}$" (hat on subscript I?)?

@@

\item[f.] page 6, column 2, line 32: is the "iid" property valid across the indices i, i.e., the n vectors have to be independent? If so, this would invalidate the use of a Sobol' sequence to create these vectors, so please clarify this point.
\item[g.] page 9, column 2 , "real case model". There are some imprecisions in this part: lines 15-16, it should be the "discounted payoff" and not just "payoff", rho is the risk-free interest rate (not just interest rate). More importantly, the authors directly give the discounted payoff in terms of the Brownian motion without stating what model is used for the stock price and without stating that for the purpose of pricing one should work under the risk-neutral measure. Please clarify this so that the financial motivation for this problem is properly done.

{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections.} 
\end{itemize}

@@

@@

@@

However, that is not a concerns since error bounds for any estimator can be calculated. That is, our algorithm can be adapted to any Sobol' index estimator. In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5).}

@@

{\color{blue} We agree with the reviewer that the effective dimension of the higher dimensions integrand might be lower than its lower dimensions counterpart. However, evaluating the effective dimension of each integrands already requires a large number of model evaluations itself (\textit{c.f.} Wang. X and Fang. K.-T., 2003).

@@

{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. There were no drastic changes observed. As a matter of fact, the failure rates have improved for all three approaches (Variant A.a, A.b and B).}

@@

{\color{blue} We understand and agree with the issue raised by the reviewer. A possible solution is to choose a higher target precision $\epsilon$ when dealing with time-expensive function. In the proposed examples, $\epsilon$ was intentionally fixed small to put forward the performance of our algorithm. To cover both situations (small and high value of $\epsilon$), the bratley example has been reworked.

On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of Sobol' indices should be dropped for a screening method (less accurate but less greedy). Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}
\end{itemize}

@@

{\color{blue} All minors points have been dealt with. For point c., equation (7) was replaced with the unbiased estimator of $\sigma^2$. For point e., the distinction has been noted in the paper given that notations cannot be changed (they need to match those of the sourced paper).
\end{document}

>>>>

\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\vk}{\vect{k}}
\newcommand{\vx}{\vect{x}}
\newcommand{\vI}{\vect{I}}
\newcommand{\hS}{\widehat{S}}
\newcommand{\tS}{\widetilde{S}}
\newcommand{\wcS}{\widecheck{S}}
\def\dashfill{\cleaders\hbox to 2em{-}\hfill}
\newcommand{\answer}[1]{{\color{blue} #1 }}

@@

\item[3.]The set C: In the section describing numerical results, choices are made for the parameters $\ell^*$ and $r$ which in turn define the set (cone) of functions C for which the error threshold formula (14) used to derive the algorithm holds. There should be some information in the paper on whether or not the functions considered in this section can be shown to be in this cone. This is especially important in light of the results obtained on page 10 (column 1, lines 36-38), where it looks like the error threshold was not met by the algorithm. Is it because the function is not in C?

\answer{End of section 3 and beginning of section 5}
\end{itemize}

@@

{\color{blue} The biased estimator has been replaced with the unbiased one.}
\item[c.] page 4, column 2, equation (14): it is not clear how $\ell$ is chosen on the RHS, and whether or not the inequality holds for all $\ell \leq m$ or for some specific value of $\ell$ ? Please clarify.

\answer{While the RHS holds for any $\ell_*\leq\ell\leq m$, it is definitely not clear how to proceed with the information given in the article. We added more detailed information explaining that one only needs to fix $r=m-\ell$. Once $r$ is chosen, the RHS only depends on $m$.}

\item[d.] page 4, column 2, line 42: is it not instead "...the error bound $\epsilon_{\hat{I}}$" (hat on subscript I?)?

@@

\item[f.] page 6, column 2, line 32: is the "iid" property valid across the indices i, i.e., the n vectors have to be independent? If so, this would invalidate the use of a Sobol' sequence to create these vectors, so please clarify this point.

\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We added the missing explanation indicating that we replace Owen's iid uniform points by a Sobol' sequence.}

\item[g.] page 9, column 2 , "real case model". There are some imprecisions in this part: lines 15-16, it should be the "discounted payoff" and not just "payoff", rho is the risk-free interest rate (not just interest rate). More importantly, the authors directly give the discounted payoff in terms of the Brownian motion without stating what model is used for the stock price and without stating that for the purpose of pricing one should work under the risk-neutral measure. Please clarify this so that the financial motivation for this problem is properly done.

{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
\end{itemize}

@@

\answer{More details have been provided in Section 3.1 to help readers follow the ideas behind the approach. Among all additions, $k_{j\ell}$ has been defined and the sums $S_m$, $\hS_{\ell,m}$, $\wcS_m$, $\tS_{\ell,m}$ have been briefly described in conjunction with the cone conditions.}

@@

\answer{
As proposed in this point, we added more information that might be useful for this issue.

If $I_1, I_2, I_3, I_4$ are all in $\mathcal{C}$, by construction we know that
\[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
However, since we do not assume the knowledge of the Walsh coefficients of our integrands, it is hard to verify whether each of them lie inside $\mathcal{C}$. Instead, we suggest and refer to some data-based necessary conditions discussed in another article. If these necessary conditions are not satisfied, one should consider enlarging the cone.}

@@

However, that is not a concern since error bounds for any estimator can be calculated. That is, our algorithm can be adapted to any Sobol' index estimator. In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5). Our goal was to design an automatic algorithm that does not ac...}

@@

{\color{blue} We agree with the reviewer that the effective dimension of the higher dimensions integrand might be lower than its lower dimensions counterpart. However, evaluating the effective dimension of each integrands already requires a large number of model evaluations (\textit{c.f.} Wang. X and Fang. K.-T., 2003).

@@

{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. There were no drastic changes observed, perhaps since the scrambling might remove most of the anchoring. Indeed, the new results show that failure rates have improved for all three approaches (Variant A.a, A.b and B).}

@@

{\color{blue} We understand and agree with the issue raised by the reviewer. A possible solution is to choose a less conservative precision $\epsilon$ when dealing with time-expensive functions. In the proposed examples, $\epsilon$ was intentionally fixed small to push forward the performance of our algorithm. That shows the difference in function evaluations cost ....

On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of a screening method is more adequate (less accurate but less greedy). Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}
\end{itemize}

@@

{\color{blue} All minors points have been dealt with. For point c., equation (7) was replaced with the unbiased estimator of $\sigma^2$. For point e., the distinction has been noted in the paper. The authors preferred to keep the notations from previous cited articles.
\end{document}
